# Meta-analysis of GxSES effects on Cognitive Ability

```{r setup, include = FALSE, cache = FALSE}
library(meta.now);
library(RefManageR)
library(metaSEM)
library("metaSEM")
library("ggplot2")
library("ggthemes")

me = "GxSES"
genbib = RefManageR::ReadBib(system.file("extdata", "general.bib", package = "meta.now"))
# 1. open the bib for this project
bib = ReadBib(system.file(paste0("extdata/", me), paste0("bib_", me, ".bib"), package = "meta.now"), check = FALSE)
BibOptions(check.entries = FALSE, style = "markdown", cite.style = "authoryear", bib.style = "numeric")

# 2. open the meta-file for this project
# meta_make()
df = gdata::read.xls(system.file(paste0("extdata/", me), paste0("data_", me, ".xlsx"), package = "meta.now"), stringsAsFactors=FALSE)
# replace spaces (which are imported as periods) with "_"
df = umx_rename(df, "_", grep="\\.");
dfUS=df[df$US==1,]
dfEU=df[df$US==0,]


# 3. # TODO Check it's all up to date
	
```
## Introduction
`r AutoCite(bib, "Bates2013", before = "e.g., ")`

## Results
```{r fig.width=3.5}
hist(df$a1)
mean(df$a1)
weighted.mean(df$a1,1/(df$k*df$a1_SE^2))

weighted.mean(dfUS$a1,1/(dfUS$k*dfUS$a1_SE^2))

weighted.mean(dfEU$a1,1/(dfEU$k*dfEU$a1_SE^2))

# two level unconditional (Random Effects meta analysis)
rmeta = meta(y = a1,v = a1_SE^2, data = df)
summary(rmeta)

# three level unconditional (intercept only)
Model0 = meta3(y = a1,v = a1_SE^2,cluster = DataID,data = df,model.name = "3 level model")
summary(Model0)

# Three level US vs. Other
Model1 = meta3(y = a1,v = a1_SE^2,x = US,cluster = DataID,data = df,model.name = "3 level model")
summary(Model1)


#weighted histogram
p = ggplot(df,aes(x=a1,weight=1/(k*a1_SE^2)))
p = p + geom_histogram(col="black",fill="light grey",bins = 15)
p = p +labs(x = "Effect size", y = "Weighted count") + xlim(c(-.2, .2))
p = p + theme_base() + theme(plot.background = element_rect( color= "white"))
p

# Weighted histogram US and not US (weight = reciprocal sampling variance)

plotUS = ggplot(dfUS, aes(x = a1, weight = 1/(a1_SE^2)))
plotUS = plotUS + geom_histogram(col = "black", fill = "light grey")
plotUS = plotUS + labs(x = "Effect size", y = "Weighted count")
plotUS = plotUS + xlim(c(-.3, .3))
plotUS = plotUS + theme_base() + theme(plot.background = element_rect( color= "white")) + ggtitle("United States")
plotUS = plotUS + theme(plot.title = element_text(hjust = 0.5))

plotEU = ggplot(dfEU, aes(x = a1, weight = 1/(a1_SE^2)))
plotEU = plotEU + geom_histogram(col = "black",fill = "light grey")
plotEU = plotEU + ggtitle("Europe and Australia")
plotEU = plotEU + labs(x = "Effect size", y= "Weighted count") + ggtitle("Europe and Australia")
plotEU = plotEU + xlim(c(-.3, .3))
plotEU = plotEU + theme_base() + theme(plot.background = element_rect(color = "white")) 
plotEU = plotEU + theme(plot.title = element_text(hjust = 0.5))

multiplot(plotUS, plotEU)

# Weighted histogram US and not US (weights = reciprocal sampling variance and 1/k)
binwidth
plotUS = ggplot(dfUS, aes(x = a1, weight = 1/(k*a1_SE^2)))
plotUS = plotUS + geom_histogram(col = "black",fill = "light grey")
plotUS = plotUS + labs(x = "Effect size", y = "Weighted count")
plotUS = plotUS + xlim(c(-.3, .3))
plotUS = plotUS + theme_base()
plotUS = plotUS + theme(plot.background = element_rect( color= "white"))
plotUS = plotUS + ggtitle("United States")
plotUS = plotUS + theme(plot.title = element_text(hjust = 0.5))

plotEU = ggplot(dfEU,aes(x=a1,weight=1/(k*a1_SE^2)))
plotEU = plotEU + geom_histogram(col="black",fill="light grey")
plotEU = plotEU + labs(x="Effect size", y="Weighted count")
plotEU = plotEU + xlim(c(-.3,.3))
plotEU = plotEU + theme_base()
plotEU = plotEU + theme(plot.background = element_rect( color= "white"))
plotEU = plotEU + ggtitle("Europe and Australia")
plotEU = plotEU + theme(plot.title = element_text(hjust = 0.5))

multiplot(plotUS,plotEU)


```

## Discussion

**Data References**

```{r results = "asis", echo = FALSE}
PrintBibliography(bib, .opts = list(check.entries = FALSE, sorting = "ynt"))
```

**References for packages and methods used**

```{r results = "asis", echo = FALSE}
PrintBibliography(genbib)
```


### Citing
1. In text `r Citet(bib, "loh")`
2. In parentheses `r AutoCite(bib, "baez/online", before = "e.g., ")`.
3. Without citing = `r NoCite(bib = bib, title = "CTAN")`
4. methods
	1. by key
	2. using `SearchBib()`
		1 by type `r Citet(bib, bibtype = "Report", .opts = list(hyperlink = "to.doc"))`.
		1. From another bibliography: `r AutoCite(bib2, title = "binary longitudinal data")`.
		2. By author: `r TextCite(bib, author = "Aristotle")`.  
		3. By other fields: `r TextCite(bib, eprinttype = "arxiv")`.

### Setting options
  * Setup chunk at the start
  * Anywhere with <code>BibOptions</code>
  * List in `.opts` argument to cite functions.
  * Can mix `"authoyear"` and `"numeric"`style.

  
## hyperlinking
1. default = open document in a new window (see `?open.BibEntry`). 
2. no link `r AutoCite(bib, location = "Uppsala", .opts = list(hyperlink = FALSE))`.

## Plots
  
```{r fig.width=3.5}
plot(cars)
```


```{r fig.height=3}
plot(cars)
```

