# Meta-analysis of GxSES effects on Cognitive Ability

```{r setup, include = FALSE, cache = FALSE}
library(meta.now); library(RefManageR)
genbib <- ReadBib(system.file("extdata", "general.bib", package = "meta.now"))
# 1. open the bib for this project
bib    <- ReadBib(system.file("extdata/GxSES", "bib_GxSES.bib", package = "meta.now"), check = FALSE)
BibOptions(check.entries = FALSE, style = "markdown", cite.style = "authoryear", bib.style = "numeric")

# 2. open the meta-file for this project
# 3. check it's all up to date
	# 1. Add any new dois for refs, report errors

```

## Introduction
`r AutoCite(bib, "Bates2013", before = "e.g., ")`



## Results
```{r fig.width=3.5}
plot(cars)
```

## Discussion

**Data References**

```{r results = "asis", echo = FALSE}
PrintBibliography(bib, .opts = list(check.entries = FALSE, sorting = "ynt"))
```

**References for packages and methods used**

```{r results = "asis", echo = FALSE}
PrintBibliography(genbib)
```


### Citing
1. In text `r Citet(bib, "loh")`
2. In parentheses `r AutoCite(bib, "baez/online", before = "e.g., ")`.
3. Without citing = `r NoCite(bib = bib, title = "CTAN")`
4. methods
	1. by key
	2. using `SearchBib()`
		1 by type `r Citet(bib, bibtype = "Report", .opts = list(hyperlink = "to.doc"))`.
		1. From another bibliography: `r AutoCite(bib2, title = "binary longitudinal data")`.
		2. By author: `r TextCite(bib, author = "Aristotle")`.  
		3. By other fields: `r TextCite(bib, eprinttype = "arxiv")`.

### Setting options
  * Setup chunk at the start
  * Anywhere with <code>BibOptions</code>
  * List in `.opts` argument to cite functions.
  * Can mix `"authoyear"` and `"numeric"`style.

  
## hyperlinking
1. default = open document in a new window (see `?open.BibEntry`). 
2. no link `r AutoCite(bib, location = "Uppsala", .opts = list(hyperlink = FALSE))`.

## Plots
  
```{r fig.width=3.5}
plot(cars)
```


```{r fig.height=3}
plot(cars)
```

